\documentclass[10pt]{article}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{lmodern}[lmss]
\usepackage{hyperref}

\geometry{a4paper, margin=0.5in}
\hfuzz=2500pt

\begin{document}

\begin{center}
{\Large\textbf{Charles Ancel}}\\
\vspace{5pt}
\small{Chicago, IL, 60611 \(\bullet\) 312.307.7780 \(\bullet\) charlesjancel@gmail.com \(\bullet\) \href{https://www.linkedin.com/in/charles-j-ancel/}{My LinkedIn}}
\end{center}

\vspace{-10pt}
\section*{Objective}
\vspace{0pt}
Statistical analyst with a strong background in data analysis, statistical modeling, and data-driven decision-making. Proficient in Excel, R, Python, and SQL, with a proven ability to apply statistical techniques to real-world problems. Seeking to leverage my analytical skills in a dynamic environment to drive impactful insights and improve decision-making processes.

\vspace{-10pt}
\section*{Education}
\vspace{0pt}
\begin{multicols}{2}
\textbf{B.Sc. in Mathematics, Minor in Economics} \\
University of Illinois, Urbana-Champaign \\
\textbf{Graduation: May 2024} \\
Relevant Coursework:
\begin{itemize}[noitemsep,nosep]
    \item Methods of Applied Statistics, Theory of Interest
    \item Game Theory, Macroeconomic Policy
    \item Intermediate Abstract Algebra, Real Analysis
\end{itemize}
\end{multicols}

\vspace{-10pt}
\section*{Work Experience}
\vspace{0pt}

\textbf{Photo Studio and Design Assistant} \hfill \textbf{Jan - Aug 2021, May - Aug 2022} \\
FTD LLC, Downers Grove, IL \\
\begin{itemize}[noitemsep,nosep]
    \item Conducted statistical analysis on product pricing data, identifying trends that led to a 15\% increase in SKU profitability.
    \item Developed and maintained Excel-based reports to analyze year-over-year changes in costs, enhancing strategic decision-making.
    \item Provided data-driven recommendations for pricing adjustments, improving overall margin performance.
\end{itemize}

\vspace{0pt}
\textbf{Logistics Coordinator} \hfill \textbf{Dec 2022 - Jan 2023, Dec 2023 - Jan 2024} \\
Tournament of Roses: Rose Parade, Pasadena, CA \\
\begin{itemize}[noitemsep,nosep]
    \item Applied data analysis techniques to optimize logistics and resource allocation, improving project efficiency by 20\%.
    \item Analyzed workflow processes to enhance team coordination and reduce project completion times.
    \item Managed data collection and validation for logistics planning, supporting real-time decision-making.
\end{itemize}

\vspace{0pt}
\textbf{Camp Counselor (Leadership Role)} \hfill \textbf{Summer 2019, Summer 2020} \\
Camp Eagle Ridge, Mellen, WI \\
\begin{itemize}[noitemsep,nosep]
    \item Designed and implemented lesson plans with a focus on leadership and teamwork, utilizing feedback data to adjust activities for improved engagement.
    \item Led both physical and educational activities, demonstrating strong interpersonal and communication skills.
\end{itemize}

\vspace{-10pt}
\section*{Projects}
\vspace{0pt}

\textbf{Monetary Policy Impact Analysis Using VAR Model} \\
Applied a Vector Autoregression (VAR) model to assess the impact of monetary policy on inflation, GDP, and unemployment using Federal Reserve data. Conducted scenario analysis to simulate economic effects, enhancing understanding of policy impacts.

\vspace{0pt}
\textbf{Floral Arrangement Data Analysis} \\
Performed statistical analysis on SKU profitability using Excel and R, identifying key drivers of performance. Created visualizations and reports to support marketing and procurement decisions.

\vspace{0pt}
\textbf{College Football Game Data Analysis} \\
Analyzed a large dataset of college football games to identify performance trends and predict outcomes. Applied regression models and data visualization tools to present insights, demonstrating the ability to apply statistical methods to sports analytics.

\vspace{-10pt}
\section*{Skills}
\vspace{0pt}
\begin{multicols}{2}
\begin{itemize}[noitemsep,nosep]
    \item Statistical Analysis (R, Python, Excel)
    \item Data Management and SQL
    \item Predictive Modeling and Forecasting
    \item Data Visualization (Tableau, Matplotlib)
    \item Report Writing and Analytical Reporting
    \item Project Management and Problem Solving
\end{itemize}
\end{multicols}

\end{document}
