\documentclass[10pt]{article}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{lmodern}[lmss]
\usepackage{hyperref}
\geometry{a4paper, margin=0.5in}
\hfuzz=2500pt
\begin{document}

\begin{center}
{\Large\textbf{Charles Ancel}}\\
\vspace{5pt}
\small{Chicago, IL, 60611 \(\bullet\) 312.307.7780 \(\bullet\) charlesjancel@gmail.com \(\bullet\) \href{https://www.linkedin.com/in/charles-j-ancel/}{My LinkedIn}}
\end{center}

\vspace{-10pt}
\section*{Objective}
\vspace{0pt}
Financial analyst with hands-on experience in budgeting, forecasting, and variance analysis. Eager to contribute to MLB's FP\&A team by leveraging data-driven insights to enhance operational performance and support strategic decision-making.

\vspace{-10pt}
\section*{Education}
\vspace{0pt}
\begin{multicols}{2}
\textbf{B.Sc. in Mathematics, Minor in Economics} \\
University of Illinois, Urbana-Champaign \\
\textbf{Graduation: May 2024} \\

Relevant Coursework:
\begin{itemize}[noitemsep,nosep]
    \item Methods of Applied Statistics, Theory of Interest
    \item Game Theory, Macroeconomic Policy
    \item Intermediate Abstract Algebra, Real Analysis
\end{itemize}
\end{multicols}

\vspace{-10pt}
\section*{Work Experience}
\vspace{0pt}
\textbf{Photo Studio and Design Assistant} \hfill \textbf{Jan - Aug 2021, May - Aug 2022} \\
FTD LLC, Downers Grove, IL \\
\begin{itemize}[noitemsep,nosep]
    \item Assisted in product photography design and setup for retail products while managing expense tracking and budget allocation for seasonal projects.
    \item Conducted profitability analysis for product SKUs, adjusting pricing models to increase margins by 15\%.
    \item Built financial reports using Excel to track product pricing and stem cost changes year over year, improving budget planning and financial visibility.
    \item Supported financial analysis and resource allocation for various design projects, optimizing budget utilization.
\end{itemize}

\vspace{10pt}
\noindent\textbf{Tournament of Roses: Logistics Coordinator} \hfill \textbf{Dec 2022 - Jan 2023, Dec 2023 - Jan 2024} \\
Pasadena, California \\
\begin{itemize}[noitemsep,nosep]
    \item Coordinated the logistics for floral designs, optimizing resource management across multiple teams and managing budget constraints for materials.
    \item Directed volunteer teams to ensure that complex design tasks were completed within tight deadlines.
    \item Improved workflow processes for team coordination, resulting in a 20\% reduction in project completion time and better adherence to budget limits.
\end{itemize}


\vspace{10pt}
\textbf{Camp Counselor} \hfill \textbf{Summer 2019, Summer 2020} \\
Campe Eagle Ridge, Mellen, WI\\
\begin{itemize}[noitemsep,nosep]
    \item Created lesson plans and managed activities for children aged 7-17, focusing on leadership development.
    \item Oversaw both physical and educational activities, ensuring that all programs were safe, engaging, and within budget.
    \item Collaborated with a team of counselors to ensure a smooth and enjoyable camp experience for participants, adhering to resource and budget constraints.
\end{itemize}

\vspace{-10pt}
\section*{Projects}
\vspace{0pt}



\textbf{Floral Arrangement Data Analysis (FTD Analyst Work)} \\
Performed data analysis on SKU profitability, conducting pricing adjustments to improve margins by 15\%. Created reports using Python and Excel to help guide marketing and procurement strategies for future retail pricing.

\vspace{0pt}
\textbf{College Football Game Data Analysis} \\
Analyzed a dataset of college football games using statistical models to identify trends in performance and predict game outcomes. Applied insights to forecast performance trends and optimize strategy recommendations.

\vspace{-10pt}
\section*{Skills}
\vspace{0pt}
\begin{multicols}{2}
\begin{itemize}[noitemsep,nosep]
    \item Financial Data Analysis (Excel, R, Python, SQL)
    \item Financial Modeling and Forecasting
    \item Statistical Analysis and Data Visualization (Excel, Tableau)
    \item Collaboration and Team Management
    \item Report Writing and Data Presentation
    \item Time Management and Multitasking
    \item Advanced Excel (Pivot Tables, VLOOKUP, Macros)
    \item Adaptable to Financial Planning Tools
\end{itemize}

\end{multicols}



\end{document}