\documentclass{article}
\usepackage{geometry}
\geometry{left=1in, right=1in, top=1in, bottom=1in}
\usepackage{enumitem}
\usepackage{hyperref}

\title{Federal Reserve Board Research Assistant Application}
\author{Charles Ancel}
\date{\today}

\begin{document}

\maketitle

\section*{Application Materials}

\subsection*{1. Resume}
% Include your resume here if you want to include it directly. Otherwise, mention it as an attachment.
\begin{itemize}
    \item Attached as a separate document: \textit{CAncel-Resume-FR:RA.pdf}
\end{itemize}

\subsection*{2. Cover Letter}
\begin{itemize}
    \item Attached as a separate document: \textit{CAncel-FR.pdf}
\end{itemize}

\section*{Short Essay Responses}

\subsection*{1. Perseverance}
During my Monetary Policy Impact Analysis project, I faced a significant challenge with data quality and missing information that disrupted the model's accuracy. Initially, my analysis of the federal funds rate and its impact on economic indicators such as inflation and GDP was hampered by gaps in historical data, requiring meticulous data cleaning and imputation techniques. I took the initiative to explore various data sources, such as FRED and alternative economic data repositories, to fill in these gaps.

I taught myself advanced imputation methods using Python and R, experimenting with multiple approaches until I found the most accurate solution for our dataset. This experience taught me the importance of perseverance and adaptability in research, especially when faced with complex data issues. The ability to navigate unfamiliar situations and seek innovative solutions will be crucial in my role as a Research Assistant, allowing me to contribute effectively to data-driven economic research.

\subsection*{2. Initiative}
As a Photo Studio and Design Assistant at FTD LLC, I frequently took the initiative to optimize our data analysis processes. One notable example was when I noticed inefficiencies in how product pricing data was managed and validated. I independently developed a set of advanced Excel-based tools, including automated reports and error-checking functions, to streamline our data validation process.

Recognizing the impact of pricing strategies on SKU profitability, I conducted additional research outside of my assigned tasks, analyzing market trends and competitor pricing. I presented my findings and suggested adjustments that led to a 15\% increase in profitability. This experience underscored my proactive nature and eagerness to engage beyond standard tasks, a mindset that I will bring to my role as a Research Assistant. My initiative will enable me to contribute fresh ideas, refine analytical methods, and actively support ongoing research projects.

\section*{Technical Skills}

\subsection*{Experience and Interest Levels}
\begin{itemize}
    \item \textbf{Compiling and Manipulating Datasets:} Moderate experience; Strong interest.
    \item \textbf{Statistical Packages:} 
        \begin{itemize}
            \item \textbf{R:} Proficient in data analysis, statistical modeling, and data visualization. Frequently used for econometric analysis, forecasting, and handling large datasets.
            \item \textbf{Stata:} No experience but willing to learn for future research tasks.
            \item \textbf{SAS:} No direct experience but open to learning as needed.
        \end{itemize}
    \item \textbf{Programming Languages:}
        \begin{itemize}
            \item \textbf{Python:} Proficient in data manipulation, statistical analysis, and data visualization. Used extensively in personal projects and academic research.
            \item \textbf{SQL:} Moderate experience in querying and managing databases, used for data extraction and data manipulation tasks.
            \item \textbf{Java:} Limited experience, mainly from academic coursework; comfortable with basic programming concepts and eager to expand this knowledge.
        \end{itemize}
    \item \textbf{Other Programs/OSs:}
        \begin{itemize}
            \item \textbf{Mathematica:} Limited experience, used for symbolic computation and solving complex mathematical problems during coursework.
            \item \textbf{Unix/Linux:} No direct experience but familiar with basic command-line operations and interested in learning for research applications.
            \item \textbf{Windows/MacOS:} Extensive experience as primary operating systems for data analysis and software use.
        \end{itemize}
\end{itemize}

\section*{Additional Information}
Please feel free to contact me if you need any additional materials or further clarification on any aspect of my application. I greatly appreciate your support and time in writing my recommendation.

\begin{flushleft}
Best regards,\\
Charles Ancel
\end{flushleft}

\end{document}
