\documentclass{letter}
\usepackage{geometry}
\geometry{left=1in, right=1in, top=1in, bottom=1in}
\signature{Charles Ancel}
\address{100 East Walton St, Apt 30CD\\Chicago, IL, 60611\\312-307-7780\\charlesjancel@gmail.com}

\begin{document}

\begin{letter}{Hiring Committee\\Federal Reserve Board\\Research Assistant Program}

    
\opening{ Dear Research Assistant Hiring Committee, }

I am writing to express my interest in the Research Assistant positions at the Federal Reserve Board. As a recent graduate with a B.Sc. in Mathematics and a minor in Economics from the University of Illinois, Urbana-Champaign, I am eager to apply my analytical skills and passion for economic research to support the Federal Reserve's mission. My strong background in statistical analysis, data management, and econometric modeling aligns well with the responsibilities of these roles, and I am excited about the opportunity to contribute to your team.

During my academic career, I developed a deep understanding of economic theory and statistical methods through rigorous coursework and hands-on research projects. For example, I applied a Vector Autoregression (VAR) model to assess the impact of monetary policy on key economic indicators such as inflation, GDP, and unemployment. This project honed my ability to work with large datasets, perform complex data analyses, and communicate findings effectively. My proficiency in Python, R, and SQL allowed me to efficiently manage data and run simulations that provided insights into economic dynamics, directly relevant to the work at the Federal Reserve.

In my role as a Photo Studio and Design Assistant at FTD LLC, I managed data validation processes and financial reconciliations, improving product pricing strategies that led to a 15\% increase in SKU profitability. These experiences taught me the importance of precision and strategic thinking, which I am eager to bring to the Research Assistant position. My analytical mindset and commitment to data integrity would be valuable assets to your research team.

What excites me most about working at the Federal Reserve is the chance to engage in research that directly informs policy decisions impacting millions of Americans. I am particularly inspired by the Federal Reserve's role in maintaining economic stability and addressing complex issues like inflation and employment. My goal is to contribute to this important work by bringing a meticulous, data-driven approach to economic research.

I am enthusiastic about joining a team that values rigorous analysis and public service as much as I do. I look forward to the opportunity to discuss how my skills, background, and dedication to economic research make me a strong candidate for this position.

Thank you for considering my application. I am eager to contribute to the Federal Reserve's mission and am available for an interview at your earliest convenience.

\begin{flushleft}
Best regards,\\
Charles Ancel
\end{flushleft}

\end{letter}

\end{document}
