\documentclass{letter}
\usepackage{geometry}
\geometry{left=1in, right=1in, top=1in, bottom=1in}
\signature{Charles Ancel}
\address{100 East Walton St, Apt 30CD\\Chicago, IL, 60611\\312-307-7780\\charlesjancel@gmail.com}

\begin{document}

\begin{letter}{Hiring Manager\\Equity Residential\\Chicago, IL}

\opening{Dear Hiring Manager,}

I am excited to apply for the Pricing Analyst position at Equity Residential, as advertised. Recently, I had a chance to connect with Barry Altshuler over the weekend, and he spoke very highly of the company and the potential opportunities at Equity Residential. With a Bachelor's degree in Mathematics and a minor in Economics from the University of Illinois at Urbana-Champaign, coupled with strong analytical skills and a keen eye for detail, I am eager to contribute to your dynamic team.

During my time as a Photo Studio Assistant at FTD, I developed and managed data workflows, ensuring the efficient execution of tasks using advanced Excel functions such as pivot tables, VLOOKUPs, and macros. These experiences honed my organizational skills and ability to handle multiple tasks under tight deadlines, ensuring accuracy and compliance.

Additionally, I have undertaken several projects that required strong analytical and data interpretation skills. Notably, my project on Floral Arrangement Data Analysis involved conducting comprehensive data analysis on SKU profitability, focusing on key trends and preferences in floral arrangements. I utilized statistical techniques and created visualizations to present insights effectively, leading to actionable recommendations for marketing campaigns and procurement strategies.

Furthermore, my project on Competitive Valorant Match Analysis involved developing a Python-based tool for scraping match data and employing statistical methods to merge datasets for comprehensive analysis. This experience has equipped me with the ability to analyze large datasets, identify trends, and provide data-driven insights.

My academic background includes coursework in statistical modeling and data interpretation, such as STAT 420 (Methods of Applied Statistics) and ECON 437 (Game Theory). These courses have provided me with a solid foundation in analytical thinking and problem-solving, which I am eager to apply in the Pricing Analyst role at Equity Residential.

I am particularly drawn to this position because of Equity Residential's commitment to creating thriving communities and its focus on innovation. I am excited about the opportunity to collaborate with various departments to develop and execute pricing strategies that maximize value and enhance returns for every asset within the portfolio. My proactive approach, strong communication skills, and ability to think creatively make me a great fit for this role.

In addition to the Pricing Analyst position, I am open to any analyst position on the team, including the Investment Analyst role that is currently open. I am enthusiastic about the opportunity to contribute to Equity Residential in any capacity that aligns with my skills and experiences.

Thank you for considering my application. I look forward to the opportunity to discuss how my background, skills, and experiences align with the needs of Equity Residential. I am available for an interview at your earliest convenience and can be reached at 312-307-7780 or via email at charlesjancel@gmail.com.

\begin{flushleft}
Best regards,\\
Charles Ancel
\end{flushleft}

\end{letter}

\end{document}
