\documentclass{letter}
\usepackage{geometry}
\geometry{left=1in, right=1in, top=1in, bottom=1in}
\signature{Charles Ancel}
\address{100 East Walton St, Apt 30CD\\Chicago, IL, 60611\\312-307-7780\\charlesjancel@gmail.com}

\begin{document}

\begin{letter}{Hiring Manager\\EPIC Insurance Brokers \& Consultants}

\opening{Dear Hiring Manager,}

I am excited to apply for the Actuarial Analyst (Property \& Casualty) position at EPIC Insurance Brokers \& Consultants, as advertised. With a Bachelor's degree in Mathematics with a minor in Economics from the University of Illinois at Urbana-Champaign and progress toward the ACAS designation, I am eager to contribute my analytical skills and passion for risk management to your dynamic team.

In my previous role as a Photo Studio Assistant at FTD, I gained valuable experience in managing data, conducting detailed analyses, and optimizing workflows to ensure efficiency and accuracy. I also developed strong problem-solving and communication skills, which are crucial for collaborating with diverse teams and presenting complex concepts to non-technical stakeholders. My work involved using advanced Excel functions and statistical software, which has prepared me well for the data analysis and modeling responsibilities of the Actuarial Analyst role.

My academic background has equipped me with a solid foundation in actuarial science, statistics, and data manipulation tools. Courses such as STAT 420 (Methods of Applied Statistics) and ECON 437 (Game Theory) have honed my analytical skills and my ability to apply theoretical knowledge to practical scenarios. Additionally, my experience as a camp counselor at Camp Eagle Ridge, where I planned and led activities, has further developed my organizational and leadership abilities, which I believe will be beneficial in designing and presenting customized insurance programs to clients.

I am particularly drawn to EPIC because of its commitment to innovation, diversity, and professional growth. The opportunity to work closely with broker teams to design tailored insurance solutions that meet the unique needs of corporate clients excites me. I am confident that my background, skills, and dedication to continuous learning align well with EPIC's mission and values.

Thank you for considering my application. I look forward to the opportunity to discuss how my background, skills, and experiences align with the needs of EPIC Insurance Brokers \& Consultants. I am available for an interview at your earliest convenience and can be reached at 312-307-7780 or via email at charlesjancel@gmail.com.

\begin{flushleft}
Sincerely,\\
Charles Ancel
\end{flushleft}

\end{letter}

\end{document}
