\documentclass[10pt]{article}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{lmodern}[lmss]
\usepackage{hyperref}
\geometry{a4paper, margin=0.5in}
\hfuzz=2500pt
\begin{document}

\begin{center}
{\Large\textbf{Charles Ancel}}\\
\vspace{5pt}
\small{Chicago, IL, 60611 \(\bullet\) 312.307.7780 \(\bullet\) \href{mailto:charlesjancel@gmail.com}{charlesjancel@gmail.com} \(\bullet\) \href{https://www.linkedin.com/in/charles-j-ancel/}{My LinkedIn}}
\end{center}
\vspace{-10pt}

\section*{Objective}
\vspace{0pt}
Recent Mathematics graduate with a minor in Economics and strong expertise in data analysis, seeking an Analyst role in financial services and insurance. Experienced in econometrics, statistical modeling, and delivering data-driven insights with a focus on producing client-ready reports and managing complex projects. Actively researching trends in asset management and insurance markets.

\vspace{-10pt}
\section*{Education}
\vspace{0pt}
\begin{multicols}{2}
\textbf{B.Sc. in Mathematics, Minor in Economics} \\
University of Illinois, Urbana-Champaign \\
\textbf{Graduation: May 2024} \\

Relevant Coursework:
\begin{itemize}[noitemsep,nosep]
    \item Methods of Applied Statistics, Theory of Interest
    \item Game Theory, Macroeconomic Policy
    \item Intermediate Abstract Algebra, Real Analysis
\end{itemize}
\end{multicols}

\vspace{-10pt}
\section*{Selected Projects}
\vspace{0pt}
\textbf{Monetary Policy Impact Analysis Using VAR Model} \\
Applied VAR model to assess the impact of monetary policy on inflation, GDP, and unemployment using Federal Reserve data. Conducted scenario analysis simulating interest rate impacts, producing Impulse Response Functions to visualize economic effects and assess risks relevant to insurance markets and asset management.

\vspace{0pt}
\textbf{Floral Arrangement Data Analysis (FTD Analyst Work)} \\
Performed data analysis on SKU profitability, generating insights for marketing strategies. Developed visualizations and provided actionable recommendations to enhance margins. Conducted pricing analysis, leading to a 15\% increase in SKU profitability and optimized resource allocation for future retail pricing strategies.

\vspace{0pt}
\textbf{College Football Game Analysis} \\
Used statistical models to analyze a dataset of college football games, identifying performance trends and predicting game outcomes. Demonstrated predictive modeling skills that can be applied to risk assessment in financial services.

\vspace{-10pt}
\section*{Work Experience}
\vspace{0pt}
\textbf{Photo Studio and Design Assistant} \hfill \textbf{Jan - Aug 2021, May - Aug 2022} \\
FTD LLC, Downers Grove, IL \\
\begin{itemize}[noitemsep,nosep]
    \item Assisted in the design and execution of product photography for retail designs while managing pricing analysis and resource allocation to optimize seasonal workflows.
    \item Increased SKU profitability by 15\% through pricing strategy optimization and trend analysis.
    \item Developed advanced Excel-based reports to support profitability targets for floral designs.
    \item Conducted trend analysis and pricing shifts, enabling efficient resource management.
\end{itemize}

\vspace{0pt}
\textbf{Logistics Coordinator} \hfill \textbf{Dec 2022 - Jan 2023, Dec 2023 - Jan 2024} \\
Tournament of Roses: Rose Parade, Pasadena, CA \\
\begin{itemize}[noitemsep,nosep]
    \item Managed logistics for floral designs, optimizing resource management across teams and ensuring timely execution.
    \item Directed volunteer teams, coordinating design tasks under strict deadlines, demonstrating adaptability and collaboration.
\end{itemize}

\vspace{0pt}
\textbf{Camp Counselor (Leadership Role)} \hfill \textbf{Summer 2019, Summer 2020} \\
Camp Eagle Ridge, Mellen, WI \\
\begin{itemize}[noitemsep,nosep]
    \item Created lesson plans and managed activities for children aged 7-17 over a 9-week period, fostering leadership development.
    \item Led both physical and educational activities, managing groups with diverse needs, demonstrating teamwork and communication skills
    \item Collaborated with a team of counselors, ensuring safety and engagement in a variety of programs.
\end{itemize}

\vspace{-10pt}
\section*{Skills}
\vspace{0pt}
\begin{multicols}{2}
\begin{itemize}[noitemsep,nosep]
    \item Financial Data Analysis (Excel, R, Python, SQL)
    \item Risk Analysis and Modeling (VAR, Statistical Models)
    \item Reporting and Client Presentations
    \item Market and Industry Research (Insurance, Asset Management)
    \item Team Collaboration and Project Management
    \item Data Visualization (Tableau, Power BI, Matplotlib)
\end{itemize}
\end{multicols}
\end{document}