\documentclass[10pt]{article}
\usepackage{geometry}
\geometry{a4paper, margin=0.5in}
\usepackage{enumitem}
\setlist[itemize]{align=parleft,left=0pt..1em}
\hfuzz=2500pt

\begin{document}

\begin{center}
    {\Large\textbf{Charles Ancel}}\\
    \vspace{5pt}
    \small{100 East Walton St, Apt 30CD, Chicago, IL, 60611 $\bullet$ 312-307-7780 $\bullet$ charlesjancel@gmail.com}
\end{center}

\vspace{-10pt}

\section*{Education}
\textbf{Bachelor of Science in Mathematics with Minor in Economics} \hfill \textbf{August 2024} \\
University of Illinois at Urbana-Champaign, Urbana, IL \\
\textbf{Relevant Coursework:}
\begin{itemize}
    \item Advanced Mathematical Techniques: Courses including Intermediate Abstract Algebra, Set Theory and Topology, Differential Equations, and Elementary Real Analysis.
    \item Economic Analysis \& Decision Making: Courses including Game Theory and Macroeconomic Policy.
    \item Statistical Modeling \& Data Interpretation: Courses including Methods of Applied Statistics.
\end{itemize}

\vspace{-10pt}
\section*{Professional Experience}
\textbf{Photo Studio Assistant} \hfill \textbf{January-August 2021, May-August 2022} \\
FTD, Downers Grove, IL 
\begin{itemize}
    \item Conducted comprehensive color and stem analysis for seasonal assortments using sales data.
    \item Managed workflow and pricing using advanced Excel functions such as pivot tables, VLOOKUPs, and macros to ensure profitability and efficiency.
    \item Created detailed reports and dashboards to present key metrics and insights to stakeholders.
    \item Documented year-over-year stem pricing shifts to calculate best practices for future retail pricing.
\end{itemize}

\textbf{Rose Parade Logistics Coordinator} \hfill \textbf{December 2022, December 2023}
\begin{itemize}
    \item Coordinated floral design logistics for the Rose Parade, ensuring consistency and supporting the creative vision of the design team.
    \item Acted as primary logistical coordinator below the director, optimizing allocation and management of florals and resources.
\end{itemize}

\vspace{-10pt}
\section*{Projects}
\textbf{Competitive Valorant Match Analysis} \hfill \textbf{2023}
\begin{itemize}
    \item Developed a Python-based tool for scraping competitive Valorant match data, establishing performance baselines and identifying success patterns.
    \item Employed statistical methods to merge datasets for comprehensive analysis of player and team dynamics.
\end{itemize}

\textbf{College Football Games Statistical Analysis} \hfill \textbf{2022}
\begin{itemize}
    \item Analyzed dataset covering college football games from 2001 to present, focusing on game dynamics and outcomes.
    \item Utilized statistical techniques to evaluate trends, performances, and the 'excitement index' of games.
\end{itemize}

\vspace{-10pt}
\section*{Skills}
\begin{itemize}
    \item \textbf{Programming Languages:} Python, R, SQL
    \item \textbf{Data Analysis:} Data cleaning, transformation, and visualization; statistical modeling
    \item \textbf{Tools:} Excel (advanced functions, pivot tables, VLOOKUPs, macros), Git, RStudio
    \item \textbf{Soft Skills:} Critical thinking, problem-solving, collaboration, project management
\end{itemize}

\vspace{-10pt}
\section*{Certifications}
\begin{itemize}
    \item Certification in Finite Mathematics
\end{itemize}

\vspace{-10pt}
\section*{Professional Development}
\begin{itemize}
    \item Continuous learning through online courses and workshops in data science and machine learning.
\end{itemize}

\end{document}
