---
title: "ECON425_VA2_CAncel"
author: "Charles Ancel"
date: "2024-07-15"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(fredr)
library(dplyr)

# Set your FRED API key
fredr_set_key("89e09406a6b0e5d39d06d3b19fec5156")
```

# Federal Reserve's Process for Implementing Monetary Policy

## Main Instrument of the Fed's Monetary Policy

The main instrument of the Fed's monetary policy is the federal funds rate, which is the interest rate at which banks lend reserves to each other overnight. This rate is influenced through open market operations but is not directly controlled by the Fed.

## Decision Process in FOMC Meetings

Monetary policy is decided in the Federal Open Market Committee (FOMC) meetings, where members review economic data, consider forecasts, and discuss economic conditions before voting on the appropriate level for the federal funds rate.

## Public Announcement

The monetary policy decision is announced to the public via press releases and statements from the Fed, providing transparency and managing market expectations.

## Implementation by the New York Fed’s Open Market Trading Desk

The New York Fed's Open Market Trading Desk implements the FOMC's decision by conducting open market operations, buying or selling government securities to influence the supply of reserves in the banking system.

# Objectives of Monetary Policy

## Price Stability

One of the main objectives of monetary policy is to maintain price stability, which means keeping inflation low and stable.

## Full Employment

Another objective is to achieve full employment, where all who are willing and able to work can find employment.

## Loss Function

The central bank's loss function reflects the trade-offs between these objectives. It typically includes terms for both inflation and output variability:

\[ L = \lambda (\pi_t - \pi^*)^2 + (y_t - y^*)^2 \]

where \(\pi_t\) is the inflation rate, \(\pi^*\) is the target inflation rate, \(y_t\) is the output, and \(y^*\) is the potential output.

# Term Structure of Interest Rates

## Concept of Term Structure

The term structure of interest rates, or yield curve, represents the relationship between interest rates of bonds with different maturities.

## Relevance to Monetary Policy

Monetary policy influences the term structure by setting short-term interest rates, which affect longer-term rates and help achieve the central bank's objectives.

```{r Slide-4, echo=TRUE, message=FALSE, warning=FALSE}
# Fetching nominal exchange rate and interest rate data from FRED
nominal_exchange_rate <- fredr(series_id = "DEXUSEU", observation_start = as.Date("2000-01-01"))
domestic_interest_rate <- fredr(series_id = "DGS10", observation_start = as.Date("2000-01-01"))
foreign_interest_rate <- fredr(series_id = "IR3TIB01EZM156N", observation_start = as.Date("2000-01-01"))

# Merging and calculating interest rate differential
data_exchange <- nominal_exchange_rate %>%
  rename(nominal_rate = value) %>%
  inner_join(domestic_interest_rate %>% rename(domestic_rate = value), by = "date") %>%
  inner_join(foreign_interest_rate %>% rename(foreign_rate = value), by = "date") %>%
  mutate(interest_rate_diff = domestic_rate - foreign_rate) %>%
  filter(!is.na(interest_rate_diff))

# Interpolating missing values
data_exchange <- data_exchange %>%
  mutate(interest_rate_diff = zoo::na.approx(interest_rate_diff, na.rm = FALSE))

# Checking the range of values and printing a sample
summary(data_exchange)
head(data_exchange)

# Plotting nominal exchange rate and interest rate differential with smoothing
exchange_rate_plot <- ggplot(data_exchange, aes(x = date)) +
  geom_line(aes(y = nominal_rate, color = "Nominal Exchange Rate")) +
  geom_line(aes(y = interest_rate_diff, color = "Interest Rate Differential")) +
  
  labs(title = "Nominal Exchange Rate and Interest Rate Differential (2000-2020)",
       y = "Value", x = "Year") +
  scale_color_manual(values = c("Nominal Exchange Rate" = "blue", "Interest Rate Differential" = "red"))

ggsave("Nominal_Exchange_Rate_and_Interest_Rate_Differential.png", plot = exchange_rate_plot)
exchange_rate_plot

```

Explanation: This graph shows the relationship between the nominal exchange rate (in blue) and the interest rate differential (in red) over the period from 2000 to 2020. The nominal exchange rate is influenced by the difference between domestic and foreign interest rates. When the interest rate differential increases, the nominal exchange rate typically appreciates.

# MP Curve and Optimal Monetary Policy

## Optimal Policy Representation

The MP curve shows the relationship between the real interest rate and inflation. It represents optimal policy when it aligns with the central bank's objectives.

## Non-Optimal Conditions

The MP curve may not be optimal if it doesn't account for other economic conditions or shocks, leading to excessive inflation volatility or failing to address output gaps effectively.

```{r Slide-5, echo=TRUE}
# Fetching real interest rate and inflation data from FRED
real_interest_rate <- fredr(series_id = "DFII10", observation_start = as.Date("2000-01-01"))
inflation_rate <- fredr(series_id = "CPIAUCSL", observation_start = as.Date("2000-01-01"))

# Calculating annual inflation rate
inflation_rate <- inflation_rate %>%
  mutate(inflation = (value / lag(value, 12) - 1) * 100) %>%
  filter(!is.na(inflation))

# Merging data
mp_data <- left_join(real_interest_rate, inflation_rate, by = "date") %>%
  rename(real_interest_rate = value.x, inflation = inflation) %>%
  select(date, real_interest_rate, inflation)

# Plotting MP curve
mp_curve_plot <- ggplot(mp_data, aes(x = inflation, y = real_interest_rate)) +
  geom_point(color = "blue") +
  geom_smooth(method = "lm", color = "red") +
  labs(title = "MP Curve",
       y = "Real Interest Rate (%)", x = "Inflation (%)")
ggsave("MP_Curve.png", plot = mp_curve_plot)
mp_curve_plot
```

Explanation: This graph represents the MP curve, showing the relationship between the real interest rate and inflation. The downward slope indicates that as inflation increases, the real interest rate set by the central bank decreases. The MP curve is used to illustrate how the central bank adjusts real interest rates in response to changes in inflation to stabilize the economy.

# The Taylor Rule

## Definition and Formula

The Taylor Rule provides a guideline for setting interest rates based on inflation and output gaps:

\[ i_t = r^* + \pi_t + 0.5(\pi_t - \pi^*) + 0.5(y_t - y^*) \]

where \(i_t\) is the nominal interest rate, \(r^*\) is the real equilibrium interest rate, \(\pi_t\) is the inflation rate, \(\pi^*\) is the target inflation rate, \(y_t\) is the output, and \(y^*\) is the potential output.

## Optimality and Usefulness

While not always optimal, the Taylor Rule is useful for its simplicity and transparency, helping guide expectations and improve policy credibility.

# Dangers of Not Following the Taylor Principle

## Taylor Principle Explanation

The Taylor Principle states that the central bank should raise nominal interest rates by more than the increase in inflation to stabilize the economy.

## Consequences of Ignoring the Principle

Failing to follow the Taylor Principle during high inflation can lead to runaway inflation, as real interest rates fall, boosting aggregate demand and further increasing inflation.

```{r Slide-6, echo=TRUE}
# Simulating inflation dynamics with and without the Taylor Principle
time <- 1:10
inflation_with_taylor <- exp(-0.3 * time)
inflation_without_taylor <- exp(0.3 * time)
inflation_dynamics_data <- data.frame(Time = rep(time, 2), 
                                      Inflation = c(inflation_with_taylor, inflation_without_taylor), 
                                      Scenario = rep(c("With Taylor Principle", "Without Taylor Principle"), each = 10))

inflation_dynamics_plot <- ggplot(inflation_dynamics_data, aes(x = Time, y = Inflation, color = Scenario)) +
  geom_line(size = 1) +
  labs(title = "Dynamics of Inflation with and without the Taylor Principle",
       x = "Time",
       y = "Inflation Rate")

ggsave("InflationDynamics.png", plot = inflation_dynamics_plot)
inflation_dynamics_plot
```

Explanation: This graph illustrates the dynamics of inflation with and without following the Taylor Principle. The red line shows the scenario where the Taylor Principle is followed, resulting in controlled inflation. The blue line represents the scenario without the Taylor Principle, where inflation rises exponentially over time. This demonstrates the importance of adhering to the Taylor Principle to prevent runaway inflation.

# Optimal Stabilization vs. Optimal Disinflation

## Optimal Stabilization

Optimal stabilization aims to minimize the variance of both inflation and output by responding to shocks in a balanced manner.

## Optimal Disinflation

Optimal disinflation focuses on reducing inflation to a lower target level with minimal output loss. This involves a gradual approach to avoid sharp recessions.

# Importance of Expectations

 in Macroeconomics

## Role of Expectations

Expectations about future economic conditions influence current behavior. For example, if people expect higher inflation, they may spend more now, increasing current inflation.

## Rational Expectations

Standard models assume rational expectations, meaning people use all available information to make forecasts, leading to more accurate predictions and efficient markets.

# The Lucas Critique

## Explanation of Lucas Critique

The Lucas Critique argues that traditional econometric models fail to account for changes in policy regimes because they don't consider how agents' behavior changes in response to new policies.

## Importance for Policy Making

This critique highlights the need for models that incorporate rational expectations and policy impacts on behavior.

# Central Bank Preferences and Policy

## Dangers of Alignment

A central bank too aligned with public preferences may prioritize short-term gains over long-term stability, leading to inflationary policies and economic instability.

## Solution: Central Bank Independence

Appointing a conservative central banker who prioritizes inflation control over output stabilization can help mitigate this risk, balancing long-term stability with short-term flexibility.

# Conclusion

Thank you for your attention. This concludes my discussion on monetary policy concepts. I hope this has provided a clear and comprehensive understanding of the topics. If you have any questions, please feel free to ask.