\documentclass{letter}
\usepackage{geometry}
\geometry{left=1in, right=1in, top=1in, bottom=1in}
\signature{Charles Ancel}
\address{100 East Walton St, Apt 30CD\\Chicago, IL, 60611\\312-307-7780\\charlesjancel@gmail.com}

\begin{document}

\begin{letter}{Eric Noll\\Center for Neighborhood Engaged Research \& Science (CORNERS)\\Northwestern University\\Evanston, IL}

\opening{Dear Eric Noll,}

I am writing to express my interest in the Data Analyst position at the Center for Neighborhood Engaged Research \& Science (CORNERS) at Northwestern University, as advertised. With a Bachelor's degree in Mathematics and a minor in Economics from the University of Illinois at Urbana-Champaign, coupled with my experience in data analysis, statistical methods, and programming, I am excited about the opportunity to contribute to your team.

In my academic and professional career, I have developed strong skills in data cleaning, transformation, and analysis, utilizing tools such as Python and R. My proficiency in these programming languages has enabled me to perform complex data mining, data modeling, and statistical analyses. For example, during my tenure as a Photo Studio Assistant at FTD, I conducted a comprehensive color and stem analysis for seasonal assortments, involving data cleaning, merging datasets from multiple sources, and using statistical methods to derive actionable insights. This experience has equipped me with the critical thinking and problem-solving skills necessary for this role.

I am particularly drawn to this position at CORNERS due to its focus on addressing pressing social issues such as gun violence through Neighborhood Science. The opportunity to work closely with community and civic partners to collect and analyze a wide range of data aligns perfectly with my passion for using data to drive social change. I am adept at developing standardized templates, policies, and procedures for reporting, and have a proven track record of compiling reports, charts, and tables based on established statistical methods.

At Northwestern University, I am eager to leverage my skills to support the strategic planning, development, and performance tasks outlined in the job description. My strong organizational skills, attention to detail, and ability to collaborate effectively with team members make me confident in my ability to contribute positively to CORNERS' mission.

Thank you for considering my application. I look forward to the opportunity to discuss how my background, skills, and experiences align with the needs of your team. I am available for an interview at your earliest convenience and can be reached at 312-307-7780 or via email at charlesjancel@gmail.com.

\begin{flushleft}
Sincerely,\\
Charles Ancel
\end{flushleft}

\end{letter}

\end{document}
