\documentclass{letter}
\usepackage{graphicx}
\usepackage{geometry}
\geometry{left=1in, right=1in, top=1in, bottom=1in}
\signature{Charles Ancel}
\address{100 East Walton St, Apt 30CD\\Chicago, IL, 60611\\312-307-7780\\charlesjancel@gmail.com}

\begin{document}

\begin{letter}{Hiring Manager\\DraftKings\\Boston, MA, USA}

\opening{Dear Hiring Manager,}

I am writing to express my interest in the iGaming Marketing \& Operations Analyst position at DraftKings, as advertised. With a solid background in data analysis and a passion for the gaming industry, I am excited about the opportunity to contribute to DraftKings' mission of delivering extraordinary sports and entertainment experiences.

I hold a Bachelor's degree in Mathematics with a minor in Economics from the University of Illinois at Urbana-Champaign. My academic training has equipped me with strong analytical and problem-solving skills, particularly in the areas of statistical modeling and data interpretation. Additionally, I have over six months of professional analytics experience, where I have honed my skills in SQL and data visualization tools such as Tableau.

In my previous roles, I have supported various teams in planning, setup, and execution of data-driven initiatives. My proficiency in SQL has enabled me to develop code for the deployment and analysis of promotional campaigns, while my experience with data visualization tools has allowed me to deliver actionable insights through comprehensive reports and dashboards. I am adept at managing multiple priorities and thrive in fast-paced environments, which aligns well with the dynamic nature of the iGaming industry.

I am particularly drawn to this position at DraftKings because of your commitment to innovation and creating unforgettable moments for customers. I am eager to support the iGaming promotions teams by providing insights and recommendations that drive higher ROI. My ability to collaborate effectively with cross-functional teams, combined with my passion for casino games, makes me a strong fit for this role.

Thank you for considering my application. I am looking forward to the opportunity to discuss how my education, experience, and skills could be beneficial to the DraftKings team. I am available for an interview at your earliest convenience and can be reached at 312-307-7780 or via email at charlesjancel@gmail.com.

\begin{flushleft}
Sincerely,\\
Charles Ancel
\end{flushleft}

\end{letter}

\end{document}
