---
title: "ECON203 HW1"
author: "Charles Ancel"
output: pdf_document
date: "2024-01-27"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(repos = c(CRAN = "https://cloud.r-project.org/"))
```

```{r install}
install.packages("readxl")

# Load the package into R
library(readxl)

```

```{r load}
# Load the dataset
housing_data <- read_excel("housing.xls")
```

### Question One:

```{r plot-histogram-price}
# Plotting histogram of price
hist(housing_data$price, main="Histogram of House Prices", xlab="Price in thousands of dollars", col="blue", border="black")
```

```{r plot-price-vs-sqft}
# Plotting price vs. square feet
plot(housing_data$sqrft, housing_data$price, main="Price vs. Square Feet", xlab="Square Feet", ylab="Price (in $1000s)", pch=19)
```
```{r plot-price-vs-lotsize}
# Plotting price vs. lot size
plot(housing_data$lotsize, housing_data$price, main="Price vs. Lot Size", xlab="Size of the lot in square feet", ylab="Price in thousands of dollars", pch=19)
```
```{r plot-price-vs-bdrms}
# Plotting price vs. number of bedrooms
plot(housing_data$bdrms, housing_data$price, main="Price vs. Number of Bedrooms", xlab="Number of bedrooms", ylab="Price in thousands of dollars", pch=19)
```


```{r plot-price-vs-assess}
# Plotting price vs. assessed price
plot(housing_data$assess, housing_data$price, main="Price vs. Assessed Price", xlab="Assessed price in thousands of dollars", ylab="Price in thousands of dollars", pch=19)
abline(0, 1, col="red") # Adding a 45-degree line
```


```{r plot-histogram-colonial}
# Histogram for prices of colonial houses
hist(housing_data$price[housing_data$colonial == 1], main="Prices of Colonial Houses", xlab="Price in thousands of dollars", col="green", border="black")

# Histogram for prices of non-colonial houses
hist(housing_data$price[housing_data$colonial == 0], main="Prices of Non-Colonial Houses", xlab="Price in thousands of dollars", col="orange", border="black")
```

```{r summary-all-variables}
head(housing_data)

summary(housing_data)
```

```{r sd-all-variables}
# Standard deviation for all variables
sapply(housing_data, sd, na.rm = TRUE)
```
### Question Two:

```{r assess-symmetry}
library(e1071)
# Skewness of the price distribution
skewness_price <- skewness(housing_data$price)
print(paste("Skewness of Price: ", skewness_price))
```

```{r compare-mean-median}
mean_price <- mean(housing_data$price)
median_price <- median(housing_data$price)
print(paste("Mean Price: ", mean_price))
print(paste("Median Price: ", median_price))
```
#### (b) The price average in the dataset is 293.55 dollars.

#### (c) The price average in the dataset is smaller than the median price.


```{r price-sd}
sd_price <- sd(housing_data$price)
print(paste("Standard Deviation of Price: ", sd_price))
```
#### (d) The integer part of the price standard deviation in the dataset is 102.

### Question Three:

#### (a) The relation between prices and house size seems to be quadratic.

#### (b) There is one outlier observation in the plot of price against lotsize.

#### (c) Most houses have 3 or 4 bedrooms.

```{r bedroom-distribution}
table(housing_data$bdrms)
barplot(table(housing_data$bdrms), main="Distribution of Bedrooms", xlab="Number of Bedrooms", ylab="Frequency")
```
#### (d) Assessed prices are usually smaller than the selling prices.

### Question Four:

#### (a) Colonial houses are, on average, more expensive than non-colonial houses.
```{r colonial-noncolonial-price}
mean_price_colonial <- mean(housing_data$price[housing_data$colonial == 1])
mean_price_noncolonial <- mean(housing_data$price[housing_data$colonial == 0])
print(paste("Mean Price - Colonial: ", mean_price_colonial))
print(paste("Mean Price - Non-Colonial: ", mean_price_noncolonial))
```

#### (b) The price variance of colonial houses is smaller than the non-colonial ones.
```{r colonial-noncolonial-variance}
var_price_colonial <- var(housing_data$price[housing_data$colonial == 1])
var_price_noncolonial <- var(housing_data$price[housing_data$colonial == 0])
print(paste("Variance of Price - Colonial: ", var_price_colonial))
print(paste("Variance of Price - Non-Colonial: ", var_price_noncolonial))
```

#### (c) The price distribution of colonial houses is very different from that of non-colonial ones.


#### (d) On average, colonial houses have more bedrooms than non-colonial ones.
```{r colonial-noncolonial-bedrooms}
mean_bdrms_colonial <- mean(housing_data$bdrms[housing_data$colonial == 1])
mean_bdrms_noncolonial <- mean(housing_data$bdrms[housing_data$colonial == 0])
print(paste("Mean Bedrooms - Colonial: ", mean_bdrms_colonial))
print(paste("Mean Bedrooms - Non-Colonial: ", mean_bdrms_noncolonial))
```


