\documentclass{letter}
\usepackage{graphicx}
\usepackage{geometry}
\geometry{left=1in, right=1in, top=1in, bottom=1in}
\signature{Charles Ancel}
\address{100 East Walton St, Apt 30CD\\Chicago, IL, 60611\\312-307-7780\\charlesjancel@gmail.com}

\begin{document}

\begin{letter}{Hiring Manager\\American Bar Association\\321 North Clark\\Chicago, Illinois, USA}

\opening{Dear Hiring Manager,}

I am writing to express my interest in the Junior Business Intelligence Analyst position at the American Bar Association (ABA), as advertised. With a strong background in data analytics, a degree in Mathematics with a minor in Economics from the University of Illinois at Urbana-Champaign, and hands-on experience in data analysis and visualization, I am excited about the opportunity to contribute to ABA's mission of ensuring access to justice and promoting legal standards.

During my academic career, I engaged with complex problem-solving through advanced mathematical techniques and gained insights into economic strategies and decision-making processes. My coursework in statistical modeling and data interpretation has equipped me with robust skills in data analysis and modeling. In addition to my academic training, I have over three years of meaningful experience in analytics, where I have honed my skills in data visualization, programming, and database querying.

In my previous role as a Photo Studio Assistant at FTD, I managed workflow and pricing in Excel, ensuring profitable targets were met. This experience, along with my role as a key logistical coordinator for the Rose Parade, has strengthened my organizational and communication skills. I am proficient in Python and its data analytics packages, including Pandas, Numpy, and Scipy, and have experience creating custom dashboards using Tableau and querying databases with SQL.

I am particularly drawn to this position at the ABA because of your commitment to eliminating bias, enhancing diversity, and advancing the rule of law. I am eager to contribute to your efforts by assisting in the development of performance reports, custom dashboards, and data governance initiatives. My ability to explain complex data insights in simple terms to non-technical audiences will ensure that stakeholders can easily understand and utilize the information provided.

Furthermore, my experience in training stakeholders on self-service technologies and in-house developed analytical products aligns with the responsibilities outlined in the job description. My proficiency in Microsoft Excel, including VLOOKUPs, pivot tables, and macros, further complements my technical skill set, ensuring that I can provide excellent customer service and meet stakeholders' needs in a timely and courteous manner.

Thank you for considering my application. I am looking forward to the opportunity to discuss how my education, experience, and skills could be beneficial to the ABA team. I am available for an interview at your earliest convenience and can be reached at 312-307-7780 or via email at charlesjancel@gmail.com.

\begin{flushleft}
    Sincerely,\\
    Charles Ancel
    \end{flushleft}
\end{letter}


\end{document}
