\documentclass{letter}
\usepackage{geometry}
\geometry{left=1in, right=1in, top=1in, bottom=1in}
\signature{Charles Ancel}
\address{Chicago, IL, 60611\\312-307-7780\\charlesjancel@gmail.com}

\begin{document}

\begin{letter}{Hiring Manager\\Triad Financial Services\\Bourbonnais, IL 60914}

\opening{Dear Hiring Manager,}

I am excited to apply for the Originations Data Entry Associate position at Triad Financial Services, as advertised. With a strong background in data analysis, workflow management, and a keen eye for detail, I am confident in my ability to contribute effectively to your team and support the loan origination process.

During my time as a Photo Studio Assistant at FTD, I developed excellent organizational and data management skills. My responsibilities included setting up equipment, managing equipment storage, and editing and retouching photos. Additionally, I handled workflow and pricing using advanced Excel functions such as pivot tables, VLOOKUPs, and macros. These experiences have honed my ability to process data accurately and efficiently, ensuring compliance with all regulatory requirements.

In my academic career, I have taken courses that provided me with a solid foundation in statistical analysis and data interpretation, such as STAT 420 (Methods of Applied Statistics) and STAT 207 (Data Science Exploration). These courses have equipped me with the analytical skills needed to evaluate creditworthiness and process loan applications and documentation effectively.

One of my significant projects involved conducting a detailed analysis of college football games data, where I utilized statistical techniques to evaluate trends, performances, and the 'excitement index' of games. This project required meticulous attention to detail and the ability to handle large datasets, skills that are directly applicable to the responsibilities of the Originations Data Entry Associate role.

I am particularly drawn to this position because of the opportunity to contribute to the company's performance goals and provide exemplary customer service. I am eager to bring my proactive approach, attention to detail, and strong analytical skills to your team. My experience with MS Office applications and my ability to communicate effectively with internal and external customers will ensure timely processing and communication of credit decisions.

Thank you for considering my application. I look forward to the opportunity to discuss how my background, skills, and experiences align with the needs of Triad Financial Services. I am available for an interview at your earliest convenience and can be reached at 312-307-7780 or via email at charlesjancel@gmail.com.

\begin{flushleft}
Sincerely,\\

Charles Ancel
\end{flushleft}

\end{letter}

\end{document}
