\documentclass{letter}
\usepackage{geometry}
\geometry{left=1in, right=1in, top=1in, bottom=1in}
\signature{Charles Ancel}
\address{100 East Walton St, Apt 30CD\\Chicago, IL, 60611\\312-307-7780\\charlesjancel@gmail.com}

\begin{document}

\begin{letter}{Hiring Manager\\Inspire11\\Chicago, IL}

\opening{Dear Hiring Manager,}

I am excited to apply for the Data Science Consultant position at Inspire11. With a Bachelor's degree in Mathematics and a minor in Economics from the University of Illinois at Urbana-Champaign, and over two years of experience in data science, I am confident in my ability to contribute effectively to your team of innovative thinkers and problem solvers.

My professional background includes extensive experience in SQL and Python, as well as hands-on expertise in machine learning algorithms, hypothesis testing, and advanced analytics. In my previous role, I successfully led data science projects from scoping to solution, creating actionable data science roadmaps and business cases that significantly optimized business processes. My ability to communicate complex methodologies to non-technical audiences and deploy models into production environments has been a key factor in my success.

I am particularly drawn to Inspire11 because of its vibrant company culture, commitment to professional growth, and respect for work-life balance. The opportunity to work with a diverse team to push the boundaries of what’s possible aligns perfectly with my passion for continuous learning and innovation. I am excited about the prospect of partnering with clients to define their data and digital strategies, and to use my skills to identify and implement the right data science and machine learning solutions for their problems.

One of my notable projects involved working as a Photo Studio Assistant at FTD, where I performed a comprehensive color and stem analysis for seasonal assortments. This project required meticulous data cleaning, merging datasets from multiple sources, and utilizing statistical methods to derive actionable insights. This experience honed my critical thinking, problem-solving, and data visualization skills, which I believe will be valuable in addressing the complex business challenges faced by Inspire11's clients.

Thank you for considering my application. I am eager to bring my expertise in data science to Inspire11 and contribute to its mission of driving impactful and innovative solutions. I look forward to the opportunity to discuss how my background, skills, and experiences align with the needs of your team. I am available for an interview at your earliest convenience and can be reached at 312-307-7780 or via email at charlesjancel@gmail.com.

\begin{flushleft}
Sincerely,\\
Charles Ancel
\end{flushleft}

\end{letter}

\end{document}
