\documentclass{letter}
\usepackage{geometry}
\geometry{left=1in, right=1in, top=1in, bottom=1in}
\signature{Charles Ancel}
\address{100 East Walton St, Apt 30CD\\Chicago, IL, 60611\\312-307-7780\\charlesjancel@gmail.com}

\begin{document}

\begin{letter}{Hiring Manager\\Northwestern University\\Department of Urology}

\opening{Dear Hiring Manager,}

I am writing to express my interest in the Data Analyst position in the Department of Urology at Northwestern University, as advertised. With a Bachelor's degree in Mathematics and a minor in Economics from the University of Illinois at Urbana-Champaign, along with my experience in data analysis, statistical methods, and software proficiency, I am excited about the opportunity to contribute to your team.

In my academic and professional career, I have developed strong skills in data cleaning, transformation, and analysis. I am proficient in Python, R, and shell scripting, and have used these tools to perform complex data mining and statistical analyses. For instance, during my tenure as a Photo Studio Assistant at FTD, I performed a comprehensive color and stem analysis for seasonal assortments, which involved extensive data cleaning, merging datasets from multiple sources, and using statistical methods to derive actionable insights. This experience has equipped me with the critical thinking and problem-solving skills necessary to succeed in this role.

At Northwestern University, I am particularly drawn to the opportunity to work with diverse datasets from various sources and contribute to the development and implementation of business solutions. I am adept at developing standardized templates, policies, and procedures for reporting, and have a proven track record of compiling reports, charts, and tables based on established statistical methods. My strong organizational skills, attention to detail, and ability to collaborate effectively with team members make me confident in my ability to contribute positively to your department.

I am excited about the prospect of leveraging my skills to support the Department of Urology in its mission to deliver high-quality healthcare and advance medical research. I am also eager to take advantage of the professional growth and development opportunities offered by Northwestern University.

Thank you for considering my application. I look forward to the opportunity to discuss how my background, skills, and experiences align with the needs of your team. I am available for an interview at your earliest convenience and can be reached at 312-307-7780 or via email at charlesjancel@gmail.com.

\begin{flushleft}
Sincerely,\\
Charles Ancel
\end{flushleft}

\end{letter}

\end{document}
