\documentclass{article}
\usepackage{geometry}
\geometry{left=1in, right=1in, top=1in, bottom=1in}

\begin{document}

\section*{Personal Statement}

During my time at the University of Illinois at Urbana-Champaign, I faced significant personal challenges, including a struggle with depression. In an attempt to graduate within four years, I overloaded my schedule, which impacted my GPA. Despite these challenges, I persevered and developed strong skills in data analysis, project management, and teamwork.

These experiences have made me resilient and taught me valuable lessons in time management, self-care, and perseverance. I am now fully committed to applying these lessons and skills to my professional career. My hands-on experience in data analysis and economic research, combined with my determination and ability to overcome obstacles, makes me confident in my ability to contribute effectively to the Bureau of Labor Statistics.

In my academic and professional career, I have planned, scheduled, and conducted data collection assignments using complex economic and statistical techniques. I have developed a proven track record of evaluating data for accuracy, making necessary adjustments, and ensuring conformance to survey requirements. My ability to follow up with respondents to ensure timely and accurate data submission has been crucial in my past roles. These skills and experiences make me well-suited for the Economist / Statistician (Economics) position.

Thank you for considering my application. I am eager to bring my skills and experiences to the Bureau of Labor Statistics and contribute to its mission of providing high-quality economic data and analysis. I look forward to the opportunity to further discuss how I can contribute to your team.

\end{document}
