\documentclass{letter}
\usepackage{graphicx}
\usepackage{geometry}
\geometry{left=1in, right=1in, top=1in, bottom=1in}
\signature{Charles Ancel}
\address{100 East Walton St, Apt 30CD\\Chicago, IL, 60611\\312-307-7780\\charlesjancel@gmail.com}

\begin{document}

\begin{letter}{Hiring Manager\\Uline\\Corporate Headquarters\\12575 Uline Drive\\Pleasant Prairie, WI 53158}

\opening{Dear Hiring Manager,}

I am writing to express my interest in the Junior Inventory Control Analyst position at Uline, as advertised. With a strong background in data analysis and process optimization, a degree in Mathematics with a minor in Economics from the University of Illinois at Urbana-Champaign, and hands-on experience in inventory management and logistics, I am excited about the opportunity to contribute to Uline's mission of operational excellence.

During my academic career, I developed robust analytical skills through advanced coursework in statistical modeling and data interpretation. My hands-on experience in managing workflow and pricing in Excel during my role as a Photo Studio Assistant at FTD, combined with my responsibilities as a logistical coordinator for the Rose Parade, has equipped me with the necessary skills to review and report daily inventory adjustments and changes effectively.

In my previous roles, I have demonstrated my ability to audit operational processes and compliance procedures, identify root causes of discrepancies, and develop solutions. My proficiency in data analysis tools such as Python and SQL has enabled me to provide actionable insights and recommend process changes or system enhancements based on my findings.

I am particularly drawn to this position at Uline because of your commitment to operational excellence and the collaborative work environment. I am eager to work with the fulfillment operations team to resolve inventory discrepancies, conduct root cause analysis, and prepare comprehensive summaries related to inventory accuracy. My strong problem-solving skills, attention to detail, and ability to work effectively with cross-functional teams make me a strong fit for this role.

Thank you for considering my application. I am looking forward to the opportunity to discuss how my education, experience, and skills could be beneficial to the Uline team. I am available for an interview at your earliest convenience and can be reached at 312-307-7780 or via email at charlesjancel@gmail.com.

\begin{flushleft}
Sincerely,\\
Charles Ancel
\end{flushleft}

\end{letter}

\end{document}
