\documentclass{letter}
\usepackage{graphicx}
\usepackage{geometry}
\geometry{left=1in, right=1in, top=1in, bottom=1in}
\signature{}
\address{100 East Walton St, Apt 30CD\\Chicago, IL, 60611\\312-307-7780\\charlesjancel@gmail.com}

\begin{document}

\begin{letter}{Hiring Manager\\Core Specialty\\Chicago, IL}

\opening{Dear Hiring Manager,}

I am writing to express my interest in the Actuarial Data Analyst position at Core Specialty, as advertised. With a strong background in data analytics, a degree in Mathematics with a minor in Economics from the University of Illinois at Urbana-Champaign, and hands-on experience in data analysis and visualization, I am excited about the opportunity to contribute to your growing Actuarial Data Analytics team.

During my academic career, I engaged with complex problem-solving through advanced mathematical techniques and gained insights into economic strategies and decision-making processes. My coursework in statistical modeling and data interpretation has equipped me with robust skills in data analysis and modeling. Additionally, my hands-on experience with tools such as Python, R, SQL, and Tableau has enabled me to convert raw data into actionable insights effectively.

In my previous role as a Photo Studio Assistant at FTD, I managed workflow and pricing in Excel, ensuring profitable targets were met. This experience, along with my role as a key logistical coordinator for the Rose Parade, has strengthened my organizational and communication skills. I have developed proficiency in various data manipulation tools and have a keen eye for identifying and correcting data issues. My ability to transform data into visualized representations that convey clear understanding aligns well with the technical knowledge required for this role.

I am particularly drawn to this position at Core Specialty because of your commitment to maintaining a culture that abides by core values and supports high-level talent. I embrace the “bring-it-on” attitude and am eager to contribute to the continuous improvement and automation of data processes. My intellectual curiosity drives me to uncover patterns and trends in data, ensuring that I provide valuable insights for decision-making.

Furthermore, I am adept at breaking down complex questions into manageable tasks and providing end-to-end solutions for expedited requests. My ability to collaborate effectively with colleagues across various functional areas, combined with my willingness to grow and adapt to new techniques and tools, makes me a strong fit for your team.

Thank you for considering my application. I am looking forward to the opportunity to discuss how my education, experience, and skills could be beneficial to the Core Specialty team. I am available for an interview at your earliest convenience and can be reached at 312-307-7780 or via email at charlesjancel@gmail.com.

\begin{flushleft}
Sincerely,\\
Charles Ancel
\end{flushleft}

\end{letter}

\end{document}
