\documentclass{letter}
\usepackage{graphicx}
\usepackage{geometry}
\geometry{left=1in, right=1in, top=1in, bottom=1in}
\signature{Charles Ancel}
\address{100 East Walton St, Apt 30CD\\Chicago, IL, 60611\\312-307-7780\\charlesjancel@gmail.com}

\begin{document}

\begin{letter}{Hiring Manager\\RH\\Corte Madera, CA, United States}

\opening{Dear Hiring Manager,}

I am writing to express my interest in the Inventory Analyst position at RH, as advertised. With a strong background in data analysis, a degree in Mathematics with a minor in Economics from the University of Illinois at Urbana-Champaign, and hands-on experience in inventory management and logistics, I am excited about the opportunity to contribute to RH's mission of operational excellence and collaborative work culture.

During my academic career, I developed robust analytical skills through advanced coursework in statistical modeling and data interpretation. My hands-on experience in managing workflow and pricing in Excel during my role as a Photo Studio Assistant at FTD, combined with my responsibilities as a logistical coordinator for the Rose Parade, has equipped me with the necessary skills to assist planning managers with daily reports and manage purchase orders effectively.

In my previous roles, I have demonstrated my ability to maintain daily communication with vendors, track purchase orders, and ensure accurate data entry. My proficiency in data analysis tools such as Python and SQL has enabled me to provide actionable insights and recommend process changes or system enhancements based on my findings. I am also highly skilled in using Excel, including Pivot Tables and VLOOKUPs, which are essential for this role.

I am particularly drawn to this position at RH because of your commitment to valuing high-energy, smart, and creative individuals who are team players. I am eager to contribute to your team by assisting in the smooth and efficient delivery of products, preparing weekly transfer lists, and participating in cross-functional meetings to ensure data alignment with strategies and deadlines.

Furthermore, my strong organizational and communication skills, attention to detail, and ability to multi-task and meet deadlines make me a strong fit for this role. I am a quick learner and have a team-oriented attitude, which aligns well with the values at RH.

Thank you for considering my application. I am looking forward to the opportunity to discuss how my education, experience, and skills could be beneficial to the RH team. I am available for an interview at your earliest convenience and can be reached at 312-307-7780 or via email at charlesjancel@gmail.com.

\begin{flushleft}
Sincerely,\\
Charles Ancel
\end{flushleft}

\end{letter}

\end{document}
