\documentclass{letter}
\usepackage{geometry}
\geometry{left=1in, right=1in, top=1in, bottom=1in}
\signature{Charles Ancel}
\address{100 East Walton St, Apt 30CD\\Chicago, IL, 60611\\312-307-7780\\charlesjancel@gmail.com}

\begin{document}

\begin{letter}{Hiring Manager\\First Ascent Climbing \& Fitness\\Chicago, IL}

\opening{Dear Hiring Manager,}

I am writing to express my enthusiasm for the Hospitality Staff position at First Ascent Climbing \& Fitness, as advertised. As an avid climber and a member of First Ascent for about a year, I am excited about the opportunity to contribute to First Ascent's mission of growing a vibrant climbing community.

I have gained significant experience through various roles that required strong organizational and communication skills. For instance, during my time as a Photo Studio Assistant at FTD, I set up equipment, managed equipment storage and workflow, and edited and retouched photos. I also managed workflow and pricing using advanced Excel functions such as pivot tables, VLOOKUPs, and macros to ensure profitability and efficiency. These experiences have honed my ability to multitask, set priorities, and manage time effectively.

Additionally, I played a key role in the coordination and execution of floral designs for the Rose Parade in 2022 and 2023. In my expanded role for December 2023, I acted as the primary logistical coordinator below the director, optimizing the allocation and management of florals and resources across various parade vehicles. This role required strong organizational skills, attention to detail, and the ability to work collaboratively with a team to achieve a common goal.

Moreover, my experience as a camp counselor at Camp Eagle Ridge, a leadership camp, provided me with valuable skills in lesson planning and taking care of children. I independently ran classes and activities, ensuring that each child was engaged and learning in a safe and supportive environment. This experience has equipped me with the ability to communicate effectively with both children and adults, a skill that will be beneficial in the Hospitality Staff role at First Ascent.

I am particularly drawn to First Ascent's commitment to creating a supportive and inclusive environment for climbers of all levels. I am excited about the opportunity to contribute to this mission by providing exceptional hospitality and fostering a welcoming atmosphere. I am also eager to take on additional responsibilities, such as leading facility orientations, administering belay checks, and assisting with group events and private lessons.

Thank you for considering my application. I look forward to the opportunity to discuss how my background, skills, and experiences align with the needs of First Ascent Climbing \& Fitness. I am available for an interview at your earliest convenience and can be reached via email at charlesjancel@gmail.com, preferably, or at 312-307-7780 .

\begin{flushleft}
Sincerely,\\
Charles Ancel
\end{flushleft}

\end{letter}

\end{document}
