\documentclass[10pt]{article}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{lmodern}[lmss]
\usepackage{hyperref}

\geometry{a4paper, margin=0.5in}
\hfuzz=2500pt

\begin{document}

\begin{center}
{\Large\textbf{Charles Ancel}}\\
\vspace{5pt}
\small{Chicago, IL, 60611 \(\bullet\) 312.307.7780 \(\bullet\) charlesjancel@gmail.com \(\bullet\) \href{https://www.linkedin.com/in/charles-j-ancel/}{My LinkedIn}}
\end{center}

\vspace{-10pt}
\section*{Objective}
\vspace{0pt}
Aspiring Research Assistant with strong quantitative and analytical skills, seeking to contribute to economic research and policy analysis. Proficient in Python, R, SQL, and Excel, with hands-on experience in econometric modeling, data management, and statistical analysis.

\vspace{-10pt}
\section*{Education}
\vspace{0pt}
\begin{multicols}{2}
\textbf{B.Sc. in Mathematics, Minor in Economics} \\
University of Illinois, Urbana-Champaign \\
\textbf{Graduation: May 2024} \\
Relevant Coursework:
\begin{itemize}[noitemsep,nosep]
    \item Econometrics, Statistical Modeling
    \item Macroeconomic Policy, Game Theory
    \item Advanced Probability, Real Analysis
\end{itemize}
\end{multicols}

\vspace{-15pt}
\section*{Relevant Projects}
\vspace{0pt}

\textbf{Monetary Policy Impact Analysis Using VAR Model} \\
Personal Project \hfill \textbf{2023} \\
\begin{itemize}[noitemsep,nosep]
    \item Developed a Vector Autoregression (VAR) model to analyze the impact of changes in the federal funds rate on inflation, GDP, and unemployment.
    \item Conducted scenario analysis to simulate policy changes, providing insights into economic outcomes relevant to monetary policy decisions.
    \item Utilized Python and R for data management, statistical analysis, and visualization of results, demonstrating strong quantitative and technical skills.
\end{itemize}

\vspace{5pt}
\noindent\textbf{Floral Arrangement Data Analysis} \\
Personal Project \hfill \textbf{2022} \\
\begin{itemize}[noitemsep,nosep]
    \item Analyzed SKU profitability using statistical models to identify key performance drivers and recommend pricing adjustments.
    \item Created data visualizations to present findings effectively, enhancing decision-making in marketing and procurement.
\end{itemize}

\vspace{5pt}
\noindent\textbf{College Football Game Data Analysis} \\
Personal Project \hfill \textbf{2021} \\
\begin{itemize}[noitemsep,nosep]
    \item Used regression analysis to evaluate performance trends and predict game outcomes, applying statistical methods in a real-world context.
    \item Demonstrated ability to work with large datasets, perform detailed analysis, and communicate insights clearly.
\end{itemize}

\vspace{-10pt}
\section*{Work Experience}
\vspace{0pt}

\textbf{Photo Studio and Design Assistant} \hfill \textbf{Jan - Aug 2021, May - Aug 2022} \\
FTD LLC, Downers Grove, IL \\
\begin{itemize}[noitemsep,nosep]
    \item Managed data tracking and validation for product pricing, applying statistical techniques to improve financial outcomes.
    \item Developed Excel-based reports and conducted analysis to support pricing strategy adjustments, showcasing attention to detail and analytical skills.
\end{itemize}

\vspace{10pt}
\noindent\textbf{Logistics Coordinator} \hfill \textbf{Dec 2022 - Jan 2023, Dec 2023 - Jan 2024} \\
Tournament of Roses: Rose Parade, Pasadena, CA \\
\begin{itemize}[noitemsep,nosep]
    \item Coordinated logistics and resource allocation, utilizing data-driven decisions to enhance project efficiency by 20\%.
    \item Led volunteer teams in high-pressure environments, demonstrating strong organizational and communication skills.
\end{itemize}

\vspace{-10pt}
\section*{Skills}
\vspace{0pt}
\begin{multicols}{2}
\begin{itemize}[noitemsep,nosep]
    \item Statistical Analysis (R, Python, Excel)
    \item Data Management and SQL
    \item Econometric Modeling and Forecasting
    \item Data Visualization (Tableau, Matplotlib)
    \item Report Writing and Analytical Reporting
    \item Research and Economic Analysis
\end{itemize}
\end{multicols}

\end{document}
