\documentclass{letter}
\usepackage{graphicx}
\usepackage{geometry}
\geometry{left=1in, right=1in, top=1in, bottom=1in}
\signature{Charles Ancel}
\address{100 East Walton St, Apt 30CD\\Chicago, IL, 60611\\312-307-7780\\charlesjancel@gmail.com}

\begin{document}

\begin{letter}{Hiring Manager\\Bureau of Labor Statistics\\}

\opening{Dear Hiring Manager,}

I am writing to express my interest in the Economist / Statistician (Economics) position (Announcement number: DE-24-CHI-BLS-12449617-SAS) at the Bureau of Labor Statistics, as advertised. With a Bachelor's degree in Mathematics and a minor in Economics from the University of Illinois at Urbana-Champaign, along with my experience in data analysis and economic research, I am excited about the opportunity to contribute to your team.

In my academic and professional career, I have developed strong skills in data collection, analysis, and reporting. I have planned, scheduled, and conducted data collection assignments using complex economic and statistical techniques, ensuring reliability and accuracy in the results. My experience includes extracting data from various sources, cleaning and transforming it using statistical software such as R, and analyzing it to provide meaningful insights. In my STAT420 project, I conducted an in-depth analysis of college football game data, which involved extensive data manipulation, quality checks, and the application of statistical methods to derive valuable conclusions.

I have a proven track record of evaluating data for accuracy, making necessary adjustments, and ensuring conformance to survey requirements. My ability to follow up with respondents to ensure timely and accurate data submission has been crucial in my past roles. I am adept at using economic conditions, industry trends, and survey design specifications to recommend improvements in survey methods, ultimately enhancing data collection processes.

I am particularly drawn to this position because of the Bureau of Labor Statistics' commitment to fostering a workplace that promotes diversity, equity, inclusion, and accessibility. I am eager to contribute to your mission of protecting workers' welfare and improving working conditions by providing high-quality economic data and analysis.

Thank you for considering my application. I look forward to the opportunity to discuss how my education, experience, and skills align with the needs of your team. I am available for an interview at your earliest convenience and can be reached at 312-307-7780 or via email at charlesjancel@gmail.com.

\begin{flushleft}
Sincerely,\\
Charles Ancel
\end{flushleft}

\end{letter}

\end{document}
